%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage[inline]{enumitem}
\usepackage{listings}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Other Settings
\renewcommand\labelenumii{\alph{enumii}.}
\lstset{frame=none,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
%%%%%%%%%%%%%%%%%%%%%%%%%% Page Setting %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\geometry{letterpaper,left=0.5in,right=0.5in,top=0.5in,bottom=0.5in}
\linespread{1.15}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\underline{\textbf{Homework 1}}}
\author{Bishoy Abdelmalik}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\begin{enumerate}
    \item \begin{enumerate} \setcounter{enumii}{3}
        \item \textbf{What is the first line received from the server? } \newline HTTP/1.0 302 Found
        \item \textbf{What is the meaning of the numeric status code you receive in this line (from prior 
        question)?} \newline It means it redirected me to another location.
        \item \textbf{In general, what does the command “GET /” do? } \newline Send a get request to the root of the given domain.
        \item \textbf{Write the equivalent URL to access this site, as performed in part f…? } \newline http://www.csun.edu/
        \item \textbf{Now retry with the command “GET /xxyz.html HTTP/1.1” on line 1 (and be sure to 
        put Host: www.csun.edu on the next line) What do you receive this time?} \newline HTTP/1.1 404 Not Found and an html for the csun 404 page.
        \item \textbf{What is the meaning of the status code from part h?} \newline Requested file doesn't not found ie doesnt exist.
        \item \textbf{What web-server type and version is being run at www.csun.edu from the info 
        returned in part i?} \newline Apache/2.2.3         
    \end{enumerate}
    \item \begin{enumerate}
        \item \textbf{What is the complete path of the file djedhi.html on the server?} \newline /var/www/the/last/djedhi.html
        \item \textbf{What is the domain name of the server?} \newline adamkaplan.org
        \item \textbf{What is the protocol being used?} \newline HTTPS
        \item \textbf{What port (on the server) will the web browser try to connect to for this request?} \newline Port 443 since its an HTTPS connection. 
    \end{enumerate}
    \item \begin{enumerate}
        \item \textbf{What is the Session Transcript for the domain www.cs.ucla.edu?} \newline \begin{lstlisting}
- - - mx:www.cs.ucla.edu

1 g.edu-servers.net 192.42.93.30 NON-AUTH 34 ms Received 4 Referrals , rcode=NO_ERROR  ucla.edu. 172800 IN NS ns1.dns.ucla.edu,ucla.edu. 172800 IN NS ns2.dns.ucla.edu,ucla.edu. 172800 IN NS ns3.dns.ucla.edu,ucla.edu. 172800 IN NS ns4.dns.ucla.edu,
2 ns2.dns.ucla.edu 54.201.38.106 AUTH 72 ms Received 1 Referrals , rcode=NO_ERROR  cs.ucla.edu. 14400 IN SOA mname=NS0.CS.UCLA.EDU rname=Postmaster.CS.UCLA.EDU serial=2021030900,
LookupServer 274ms
        \end{lstlisting}
        \item \textbf{What is the Session Transcript for the fictional domain adamkaplan.org?} \newline \begin{lstlisting}
- - - mx:adamkaplan.org

1 c0.org.afilias-nst.info 199.19.53.1 AUTH 27 ms Received 1 Referrals , rcode=NAME_ERROR  org. 900 IN SOA mname=a0.org.afilias-nst.info rname=noc.afilias-nst.info serial=2014285034,
LookupServer 55ms 
       \end{lstlisting}
       \item \textbf{What is the Session Transcript for the fictional domain flatitude.google.com?} \newline \begin{lstlisting}
- - - mx:flatitude.google.com

1 f.gtld-servers.net 192.35.51.30 NON-AUTH 35 ms Received 4 Referrals , rcode=NO_ERROR  google.com. 172800 IN NS ns2.google.com,google.com. 172800 IN NS ns1.google.com,google.com. 172800 IN NS ns3.google.com,google.com. 172800 IN NS ns4.google.com,
2 ns1.google.com 216.239.32.10 AUTH 2 ms Received 1 Referrals , rcode=NAME_ERROR  google.com. 60 IN SOA mname=ns1.google.com rname=dns-admin.google.com serial=362682143,
LookupServer 104ms
       \end{lstlisting}
    \end{enumerate}
    \item \textbf{URL:} http://akaplan.edu/echo.php?a=b\&q=15\&d=funk\&c=4\&b=2\&e=z
    \item \begin{enumerate}
        \item \textbf{csun.edu} 30 hops
        \item \textbf{youtube.com} 9 hops
        \item \textbf{www.cs.vu.nl} 27 hops
    \end{enumerate}
    \item 
\end{enumerate}
\end{document}